\assignment

### 2017-03-13 project/paper.rnw
More structure.

\documentclass[11pt]{article}
\usepackage{fullpage,graphicx,float,amsmath,enumitem,fancyhdr}

@@

<<setup, echo = FALSE, message = FALSE, cache = FALSE>>=
library(knitr)
library(extrafont)
opts_chunk$set(echo = FALSE, comment = NA, message = FALSE,
               fig.path = 'proj_figure/', cache.path = 'proj_cache/',
               show.signif.stars = FALSE,
               fig.align = 'center', fig.width = 6.5, fig.height = 3,
               fig.pos = 'H', size = 'footnotesize', dev = 'pdf',
               dev.args = list(family = 'CM Roman', pointsize = 11))
knit_theme$set('print')

#library(xtable)
options(xtable.table.placement = 'H', width = 80, scipen = 2,
        show.signif.stars = FALSE)
@

@@

@@

\textcite{baddeleycoeurjolly14,baddeleyturner,diggleetal,bermanturner}

\section{Simple Example}

\section{Simulation}

>>>>

\documentclass[11pt]{article}
\usepackage{fullpage,graphicx,float,amsmath,enumitem,fancyhdr,hyperref}

@@

<<setup, echo = FALSE, message = FALSE, cache = FALSE>>=
library(knitr)
library(extrafont)
opts_chunk$set(echo = FALSE, comment = NA, message = FALSE,
               fig.path = 'paper_figure/', cache.path = 'paper_cache/',
               show.signif.stars = FALSE,
               fig.align = 'center', fig.width = 6.5, fig.height = 3,
               fig.pos = 'H', size = 'footnotesize', dev = 'pdf',
               dev.args = list(family = 'CM Roman', pointsize = 11))
knit_theme$set('print')

#library(xtable)
options(xtable.table.placement = 'H', width = 80, scipen = 2,
        show.signif.stars = FALSE)

library(spatstat)

set.seed(83534)
@

@@

unobserved point processes -- only observe events in subregions selected by
practitioner but want to make inference about inhomogeneous intensity over
entire region

know something is in the vicinity but want to know where specifically --
examples: endangered clustered plant species in underbrush of thick forest,
conservationists want to know where the clusters are; subsurface geomagnetic
anomalies that could be unexploded ordnance -- concerned with mapping the
intensity of this realization, not estimating parameters of the process

@@

\textcite{wp,digglebook,baddeleycoeurjolly14,baddeleyturner,diggleetal,bermanturner}

\section{Simple Examples}

loglinear example from HW4

<<hw4_1>>=
observe_win <- setminus.owin(owin(c(0, 1), c(0, 1)),
                             owin(c(0.5, 0.8), c(0.5, 0.8)))
predict_win <- owin(c(-0.5, 1.5), c(-0.5, 1.5))
hw4 <- rpoispp(function(x, y){exp(5 * x + 2 * y)}, win = observe_win)
par(mar = c(0, 0, 0.5, 0))
plot(hw4)
@

<<hw4_2>>=
hw4_fit <- ppm(hw4, ~ x + y, correction = 'isotropic')
hw4_pred <- predict(hw4_fit, window = predict_win, se = TRUE)
par(mfrow = c(1, 2), mar = c(0, 0, 0.5, 2))
plot(hw4_pred$estimate)
plot(observe_win, add = TRUE, col = '#ffffff40', border = NA)
points(hw4, pch = '.', col = 'white')
plot(hw4_pred$se)
plot(observe_win, add = TRUE, col = '#ffffff40', border = NA)
points(hw4, pch = '.', col = 'white')
@

easy site, realization 2,000, 390 ft spacing

\section{Simulation Study}

\section{Discussion and Conclusion}

\appendix
\section{R Code Appendix}
